Visualizations for the manuscript

### 2022-10-12 metanalysis_visualization/manuscript_Figures.Rmd
psy and no psy enconters count

```{r}
total_unique_encounters <- patient_count_psy_period_psy_all %>% 
  group_by(period) %>% 
  summarise(total_unique_encounters = sum(count_no_psy_patients + count_psy_patients))
```

@@

>>>>

```{r}
total_unique_encounters <- patient_count_psy_period_psy_all %>% 
  group_by(period) %>% 
  summarise(total_unique_encounters = sum(count_no_psy_patients + count_psy_patients), 
            psy = sum(count_psy_patients),
            percent_psy = round(psy * 100 / total_unique_encounters, 2),
            no_psy = sum(count_no_psy_patients), 
            percent_no_psy = round(no_psy * 100 / total_unique_encounters, 2)
  )
print(total_unique_encounters)
print(chisq.test(total_unique_encounters[, c("psy", "no_psy")]))

@@

```{r}
z_age <- (14.55 - 14.65) / sqrt(1.86^2/9696 + 1.79^2/11101)
pvalue_age <- 2*pnorm(z_age)
